% vim: set tw=78 sts=2 sw=2 ts=8 aw et ai:

While the simulators investigated in this paper are very useful, we believe
that there is room for improvement. Most of them are generic simulators
adapted for simulating wireless sensor networks. 
We believe that a simulator built from the beginning, having in mind that it
will be used for wireless sensors, will increase its usability and make it
possible for it to be useful in more circumstances.
We propose the following plan to build the simulator described above in a couple
of phases.
We will begin by fully designing the component architecture and basic node
structure. We will build template components and create the necessary framework to integrate them 
into a sensor node. Next we will create the necessary framework for the nodes
to communicate. 
After being able to simulate a wireless sensor network, we will implement some
routing protocols, such as LEACH and TEEN, and based on the results of the
simulation of these protocols, we will determine \codename's performance.
The final step is integrating the environment simulation into the simulator.
We will augment the simulator with environment simulation as described in the paper.
%\begin{itemize}
%  \item Component architecture and basic node structure. We will build
%  template components and create the necessary framework to integrate them
%  into a sensor node.
%  \item Comunication between nodes. Create the neccessary framework to make
%  two nodes communicate.
%  \item Implement some routing procols. To evaluate our simulator we will
%  implement some routing procols(LEACH, TEEN) in it and see it's performance
%  \item Environment simulation. Will augment the simulator with environment
%  simulation as described in the paper.
%\end{itemize}
